Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-10-29 forecast/code/figures/compare-to-hub-ryan.Rmd

# Load our HRR results ---------------------------------------------------------
```{r}
source(here::here("code", "figures", "results_processing_and_plotting.R"))
source(here::here("code", "figures", "eval_funs.R"))

actuals <- readRDS(here::here("data", "confirmed_7dav_incidence_prop.RDS"))
fcasts_honest <- readRDS(here::here("data", "results_honest.RDS")) %>%
  process_res_cases(actuals) %>%
  filter(forecaster != "gs_inherit")

fig3 <- plotter(fcasts_honest %>% filter(ahead <= 21), 
        "wis", Mean, scaler = "strawman_wis", 
        order_of_operations = c("aggr","scale")) +
  ylab("Mean WIS (relative to baseline)")
fig3
```

>>>>

# Load our HRR results ---------------------------------------------------------
```{r eval = FALSE}
source(here::here("code", "figures", "results_processing_and_plotting.R"))
source(here::here("code", "figures", "eval_funs.R"))

actuals <- readRDS(here::here("data", "confirmed_7dav_incidence_prop.RDS"))
fcasts_honest <- readRDS(here::here("data", "results_honest.RDS")) 
  process_res_cases(actuals) %>%
  filter(forecaster != "gs_subset") %>%
  filter(forecaster != "gs_inherit") %>%
  mutate(forecaster = recode(forecaster, gs = "Google-AA"))

### 2021-10-29 forecast/paper/paper.tex
Fix small typo

While forecasting carries a rich literature that offers a wide range of
techniques, see, e.g., \cite{Hyndman:2018},
we purposely constrain ourselves to 
very simple models, avoiding common enhancements such as order selection,
correction of outliers/anomalies in the data, and inclusion of regularization or
nonlinearities. For the same reason, we do not account for other factors that
may well aid in forecasting, such as age-specific effects, holiday adjustments,
public health mandates, and so on.
% Paragraph from Rob
Work in \cite{ioannidis2020a} points out many additional difficulties when it
comes to
forecasting COVID-19 case rates and deaths. These include bad data, wrong
assumptions, lack of incorporation of epidemiological features, etc.  We agree
with most of these 
and our group has found that COVID-19 forecasting to be extremely challenging.
However the point of our  paper is to demonstrate the utility of  auxiliary
indicators for improving COVID-19 forecasting, and to suggest that these
indicators might be useful for future pandemics. We are not suggesting that
these indicators make COVID-19 forecasting  easy. 
Despite these obstacles, analyses of forecasts submitted
%
to the COVID-19 Forecast Hub \cite{ForecastHub} by a large community of modelers 
have shown that simple, robust models have consistently been among the
best-performing over the pandemic, including time series models similar the ones
we use in this paper. See, e.g., \cite{Cramer:2021}, for a detailed study
of death forecasting. 
% added
Similarly, the simple autoregressive models used here for case forecasting
are competitive with top models submitted to the Forecast Hub over the same
period of time (see the Supplement for this analysis).
% Our internal evaluations suggest that the same is true (at
% least, if not to a greater extent) for case forecasting.

>>>>

While forecasting carries a rich literature that offers a wide range of
techniques, see, e.g., \cite{Hyndman:2018},
we purposely constrain ourselves to 
very simple models, avoiding common enhancements such as order selection,
correction of outliers/anomalies in the data, and inclusion of regularization or
nonlinearities. For the same reason, we do not account for other factors that
may well aid in forecasting, such as age-specific effects, holiday adjustments,
public health mandates, and so on.
% Paragraph from Rob
Work in \cite{ioannidis2020a} points out many additional difficulties when it
comes to
forecasting COVID-19 case rates and deaths. These include bad data, wrong
assumptions, lack of incorporation of epidemiological features, etc.  We agree
with most of these 
and our group has found COVID-19 forecasting to be extremely challenging.
However the point of our  paper is to demonstrate the utility of  auxiliary
indicators for improving COVID-19 forecasting, and to suggest that these
indicators might be useful for future pandemics. We are not suggesting that
these indicators make COVID-19 forecasting  easy. 
Despite these obstacles, analyses of forecasts submitted
%
to the COVID-19 Forecast Hub \cite{ForecastHub} by a large community of modelers 
have shown that simple, robust models have consistently been among the
best-performing over the pandemic, including time series models similar to the ones
we use in this paper. See, e.g., \cite{Cramer:2021}, for a detailed study
of death forecasting. 
% added
Similarly, the simple autoregressive models used here for case forecasting
are competitive with top models submitted to the Forecast Hub over the same
period of time (see the Supplement for this analysis).
% Our internal evaluations suggest that the same is true (at
% least, if not to a greater extent) for case forecasting.
